Chapter 8 - SNASS

### 2024-09-18 RQdraft2.Rmd
hwForWeek3

# Brainstorm

@@

# Research Questions (old, replace with new ones!)

@@

RQ2: To what extent does gender homophily in co-publishing influence the prestige of the publication journal?

@@

>>>>

@@

# Research Questions

@@

RQ2: How to does gender homophily affect collaboration differently for collaborations between staff who have published in low vs. high prestige journals?

@@

| Age                               | length of career                                        | time since first publication                                                                           |

### 2024-09-18 Webscraping-Chapter8-tutorial.Rmd
hwForWeek3

  time <- runif(1, 0, 8) # randomized request times bc scholar has a "trip switch" against spam 
  Sys.sleep(time)
# for every number from 1 to 10 we draw one number from 0 to 8 from a uniform distribution we put
# the wrapper sys.sleep around it that we put R to sleep for the drawn number

>>>>

  time <- runif(1, 0, 8) # randomized request times bc scholar has a "trip switch" against spam (rate limit)
  Sys.sleep(time)
# for every number from 1 to 10 we draw one number from 0 to 8 from a uniform distribution we put
# the wrapper sys.sleep around it that we put R to sleep for the drawn number
